---
title: "Nairaland ideal family size plot"
author: Casey Breen
---

Summary: Create figure comparing the distribution of stated ideal family size
in Nairaland posts (2010-2018, including coded zero/childfree ideals) with the
DHS 2018 all-women distribution (weighted, from the IPUMS-DHS extract).
Coded inputs (LLM passes under fixed codebooks; see appendix):
ideals_full_*.csv = extracted numeric ideals; zero_coded.csv = childfree pass.

```{r}
## Library packages
library(here)
source(here("code", "helpers.R"))
```

## load stated ideals

```{r}
## one row per stated ideal (numeric + childfree), assembled by
## code/scraping/5_build_coding_batches.R from the LLM coding outputs
ideals_all <- read_csv(here("data", "nairaland", "coded_output", "stated_ideals.csv"))
```

## dhs comparison

```{r}
## DHS 2018 (all women, weighted) from the IPUMS-DHS extract
dhs <- read_csv(here("data", "idhs_00002.csv"),
                col_select = c(YEAR, IDEALKID, PERWEIGHT)) %>%
  filter(YEAR == 2018, IDEALKID < 50)
dhs_mean <- weighted.mean(dhs$IDEALKID, dhs$PERWEIGHT)

## Nairaland ideals in the study window
win <- ideals_all %>% filter(post_year >= 2010, post_year <= 2018)
nl_mean <- mean(win$ideal_n)
```

## create plot


```{r}
dist <- bind_rows(
  dhs %>%
    mutate(n_cap = pmin(IDEALKID, 8)) %>%
    count(n_cap, wt = PERWEIGHT) %>%
    mutate(share = n / sum(n), src = "DHS 2018"),
  win %>%
    mutate(n_cap = pmin(ideal_n, 8)) %>%
    count(n_cap) %>%
    mutate(share = n / sum(n), src = "Nairaland")
)

nairaland_ideals_plot <- ggplot(
  dist,
  aes(n_cap, 100 * share, fill = src)
) +
  geom_col(position = "dodge", width = 0.7, alpha = 0.7, color = "black") +
  scale_fill_manual(values = c("DHS 2018" = "grey65",
                               "Nairaland" = "darkblue")) +
  scale_x_continuous(breaks = 0:8, labels = c(0:7, "8+")) +
  labs(
    x = "Ideal number of children",
    y = "Percent (%)",
    fill = NULL
  ) +
  cowplot::theme_cowplot() +
  theme(
    axis.title = element_text(face = "bold"),
    legend.position = "bottom"
  ) + 
  scale_fill_manual(
  values = c(
    "DHS 2018" = "grey65",
    "Nairaland" = "darkblue"
  ),
  labels = c(
    "DHS 2018 (mean = 6.1)",
    "Nairaland (mean = 3.3)"
  )
)

nairaland_ideals_plot

## Save plot
ggsave(plot = nairaland_ideals_plot,
       filename = here("figures", "nairaland_ideals_plot.png"),
       height = 4.8, width = 7.3, bg = "white", dpi = 300)
```

